SimBio: a flexible and extensible Python package for systems modelling

### 2023-11-14 article.qmd
Add docx format

---
title: "SimBio: a flexible and extensible Python package for systems modelling"
bibliography: bibliography.bib
format:
  html:
    number-sections: true
    anchor-sections: true
  pdf:
    documentclass: scrartcl
    papersize: a4
    geometry:
        - margin=20mm
    pdf-engine: tectonic
    number-sections: true
    colorlinks: true
---

>>>>

---
title: "SimBio: a flexible and extensible Python package for systems modelling"
bibliography: bibliography.bib
format:
  html:
    number-sections: true
    anchor-sections: true
  pdf:
    documentclass: scrartcl
    papersize: a4
    geometry:
        - margin=20mm
    pdf-engine: tectonic
    number-sections: true
    colorlinks: true
  docx:
    number-sections: true
---
